---
title: '**Supplementary Figures**'
header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
output:
  pdf_document: null
  latex_engine: pdflatex
  html_document:
    df_print: paged
---

# <manuscript title>

\newpage
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(tinytex.verbose = TRUE)
```

```{r, echo=F} 
## set up figcounter
i = 0
```

```{r, out.height="80%", echo=F,fig.align='center', warning=FALSE, message=FALSE}
knitr::include_graphics("fig/FigureS2.pdf"); i = i + 1
```

**Fig. S`r i`. Nutrient content of processed fish species**. Radars show contribution of 9 g portion to recommend intakes of each nutrient, for each sampled species. Plots coloured by processing type.

\blandscape


```{r, out.height="80%", echo=F,fig.align='center', warning=FALSE, message=FALSE}
knitr::include_graphics("fig/FigureS3.pdf"); i = i + 1
```

**Fig. S`r i`. Portion size of processed fish species required to reach recommended nutrient intakes**. Lines show the contribution to RNI (children 0.5 - 5 years old) across range in portion sizes, for each nutrient and by processing type. 15% is the RNI for a food to qualify as a source of nutrients.

\elandscape

```{r, out.height="80%", echo=F,fig.align='center', warning=FALSE, message=FALSE}
knitr::include_graphics("fig/FigureS1.pdf"); i = i + 1
```

**Fig. S`r i`. Percent change in nutrient content after processing, comparing fresh and processed samples on a wet-weight basis**.

\newpage
```{r, out.height="80%", echo=F,fig.align='center', warning=FALSE, message=FALSE}
knitr::include_graphics("fig/FigureS4.pdf"); i = i + 1
```

**Fig. S`r i`. Nutrient content of fish species by processing type**. Radars show contribution of 9 g portion to recommend intakes of each nutrient, for processing type, averaged across species.

\newpage
```{r, out.height="80%", echo=F,fig.align='center', warning=FALSE, message=FALSE}
knitr::include_graphics("fig/FigureS5.pdf"); i = i + 1
```

**Fig. S`r i`. Contaminant content of fish by processing type**. Radars show contribution of 9 g portion to maximum permissible level of three heavy metals, for each processing type, averaged across species.

\newpage

```{r, out.height="80%", echo=F,fig.align='center', warning=FALSE, message=FALSE}
knitr::include_graphics("fig/FigureS6.pdf"); i = i + 1
```

**Fig. S`r i`. Contaminant content of processed fish species**. Radars show contribution of 9 g portion to maximum permissible level of three heavy metals, for each sampled species. Plots coloured by processing type.
