---
title: '**Supplementary Figures**'
header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
output:
  pdf_document: null
  latex_engine: pdflatex
  html_document:
    df_print: paged
---

# <manuscript title>

\newpage
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(tinytex.verbose = TRUE)
```

```{r, echo=F} 
## set up figcounter
i = 0
```

```{r, out.height="80%", echo=F,fig.align='center', warning=FALSE, message=FALSE}
knitr::include_graphics("fig/FigureS1.pdf"); i = i + 1
```

**Fig. S`r i`. Nutrient content of processed fish species**. Radars show contribution of 9 g portion to recommend intakes of each nutrient, for each sampled species. Plots coloured by processing type.

\newpage

```{r, out.height="80%", echo=F,fig.align='center', warning=FALSE, message=FALSE}
knitr::include_graphics("fig/FigureS2.pdf"); i = i + 1
```

**Fig. S`r i`. Portion size of processed fish species required to reach recommended nutrient intakes**. Lines show the contribution to RNI (children 0.5 - 5 years old) across range in portion sizes, for each nutrient and by processing type. 15% is the RNI for a food to qualify as a source of nutrients.


\newpage
```{r, out.height="80%", echo=F,fig.align='center', warning=FALSE, message=FALSE}
knitr::include_graphics("fig/FigureS3.pdf"); i = i + 1
```

**Fig. S`r i`. Nutrient content of fish species by processing type**. Radars show contribution of 9 g portion to recommend intakes of each nutrient, for processing type, averaged across species.

\newpage
```{r, out.height="80%", echo=F,fig.align='center', warning=FALSE, message=FALSE}
knitr::include_graphics("fig/FigureS4.pdf"); i = i + 1
```

**Fig. S`r i`. Contaminant content of fish by processing type**. Bars show contribution of 9 g portion to exposure limits of cadmium, lead, and mercury for each processing type, averaged across species.

\newpage

```{r, out.height="80%", echo=F,fig.align='center', warning=FALSE, message=FALSE}
knitr::include_graphics("fig/FigureS5.pdf"); i = i + 1
```

**Fig. S`r i`. Contaminant content of processed fish species**. Bars show contribution of 9 g portion to exposure limits of cadmium, lead, and mercury for each sampled species, coloured by processing type.

\newpage

```{r, out.height="80%", echo=F,fig.align='center', warning=FALSE, message=FALSE}
knitr::include_graphics("fig/FigureS6.pdf"); i = i + 1
```

**Fig. S`r i`. Change in fresh fish consumption with distance to water and markets**. Lines are the posterior median probability that a household consumed fresh fish (± 95% and 50% certainty intervals), for a) distance to marine (blue) and inland (green) water and b) distance to urban centres.

\newpage

```{r, out.height="80%", echo=F,fig.align='center', warning=FALSE, message=FALSE}
knitr::include_graphics("fig/FigureS7.pdf"); i = i + 1
```

**Fig. S`r i`. Dried (a) and fresh (b) fish consumption along gradients in distance to marine (x-axis) and inland (y-axis) water**. Plot colour shows predicted median probability of fish consumption, overlaid with households from LSMS fitted to logistic models. Predictions control for effects of wealth, household size, distance to urban centres, and country.
